---
title: "Chapter 6 - Linear Model Selection and Regularization - Lab 1 - Subset Selection Methods"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
```

# Chapter 6 - Linear Model Selection and Regularization - Lab 1 - Subset Selection Methods
## Best Subset Selection
Here we apply the best subset selection approach to the **Hitters** data. We wish to predict a baseball player's **Salary** on the basis of various statistics associated with performance in the previous uear.
First of all, we note that **Salary** variable is missing for some of the players. The **is.na()** function can be used to identify the missing observations. It returns a vector of the same length as the input vector, with a **TRUE** for any elements that are missing, and a **FALSE** for non-missing elements. The **sum()** function can then be used to count all of the missing elements.

```{r}
# fix(Hitters)
names(Hitters)
dim(Hitters)
sum(is.na(Hitters$Salary))
```

Hence we see that **Salary** is missing for 59 players. The **na.omit()** function removes all of the rows that have missing values in any variable.
```{r}
Hitters = na.omit(Hitters)
dim(Hitters)
sum(is.na(Hitters$Salary))
```

The **regsubsets()** function (part of the **leaps** library) performs best subset selection by udentifying the best model that contains a given number of predictors, where *best* is quantified using RSS. The syntax is the same as for **lm()**. The **summary()** command outputs the best set of variables for each model size.
```{r}
library(leaps)
regfit.full = regsubsets(Salary~., Hitters)
summary(regfit.full)
```

An asterisk indicates that a given variable is included in the corresponding model. For instance, this output indicates that the best two-variable model contains only **Hits** and **CRBI**. By default, **regsubsets()** only reports results up to the best eight-variable model. But the **nvmax** option can be used in order to return as many variables as are desired. Here we fit up to a 19-variable model.
```{r}
regfit.full = regsubsets(Salary~., data=Hitters, nvmax=19)
reg.summary = summary(regfit.full)
```

The **summary()** function also returns R^2, RSS, adjusted R^2, Cp,, and BIC. We can examine these to try to select the *best* overall model.
```{r}
names(reg.summary)
```

For instance, we see that the R^2 statistic increases from 32%, when only one variable is included in the model, to almost 55%, when all variables are included. As expected, the R^2 statistic increases monotonically as more variables are included.
```{r}
reg.summary$rsq
```

Plotting RSS, adjusted R^2, Cp, and BIC for all of the models at once will help us decide which model to select. Note the **type="1"** option tells R to connect the plotted points with lines.
```{r}
par(mfrow=c(2, 2))
plot(reg.summary$rss, xlab="Number of Variables", ylab="RSS", type="b")
plot(reg.summary$adjr2, xlab="Number of Variables", ylab="Adjusted RSq", type="b")
```

The **points()** command works like the **plot()** command, except that is puts points on a plot that has already been created, instead of creating a new plot. The **which.max()** function can be used to identify the location of the maximum point of a vector. We will not plot a red dot to indicate the model with the largest adjusted R^2 statistic.
```{r}
plot(reg.summary$adjr2, xlab="Number of Variables", ylab="Adjusted RSq", type="b")
which.max(reg.summary$adjr2)
points(11, reg.summary$adjr2[11], col="red", cex=2, pch=20)
```

In a similar fashion we can plot the Cp and BIC statistics, and indicate the models with the smallest statistic using **which.min()**.
```{r}
par(mfrow=c(2, 2))
cp_min_index = which.min(reg.summary$cp)
plot(reg.summary$cp, xlab="Number of Variables", ylab="Cp", type="b")
points(cp_min_index, reg.summary$cp[cp_min_index], col="red", cex=2, pch=20)
bic_min_index = which.min(reg.summary$bic)
plot(reg.summary$bic, xlab="Number of Variables", ylab="BIC", type="b")
points(bic_min_index, reg.summary$bic[bic_min_index], col="red", cex=2, pch=20)

```

The **regsubsets()** function has a built-in **plot()** command which can be used to display the selected variables for the best model with a given number of predictors, ranked according to the BIC, Cp, adjusted R^2, or AIC. To find out more about this function, type **?plot.regsubsets**.
```{r}
plot(regfit.full, scale="r2")
plot(regfit.full, scale="adjr2")
plot(regfit.full, scale="Cp")
plot(regfit.full, scale="bic")

```
The top row of each plot contains a black square for each variable selected according to the optimal model associated with that statistic. For instance, we see that several models share a BIC close to -150. However, the model with the lowest BIC is the six-variable model that contains only **AtBat**, **Hits**, **Walks**, **CRBI**, **DivisionW**, and **PutOuts**. We can use the **coef()** function to see the cpefficient estimates associated with this model.
```{r}
coef(regfit.full, 6)
```
 
 
 ## Forward and Backward Stepwise Selection
 